Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2020-12-31 submission/NatCom_appendix.tex
draft for appendix figures

\begin{figure}[t]
    \centering
    \subfigure[ImageNet 1K]{
        \includegraphics[width=4.9cm]{img/all-imagenet-1k_alpha.png}
        \label{fig:imagenet1k-alpha}
    }
    \qquad
    \subfigure[ CIFAR 10 ]{
        \includegraphics[width=4.9cm]{img/all-cifar-10_alpha.png}
        \label{fig:cifar10.alpha}
    }
    \qquad
    \subfigure[ CIFAR 100 ]{
        \includegraphics[width=4.9cm]{img/all-cifar-100_alpha.png}
        \label{fig:cifar100.alpha}
    }
    \qquad
    \subfigure[ SVHN ]{
        \includegraphics[width=4.9cm]{img/all-svhn_alpha.png}
        \label{fig:svhn.alpha}
    }
    \qquad
    \subfigure[ CUB 200 ]{
        \includegraphics[width=4.9cm]{img/all-cub-200-2011_alpha.png}
        \label{fig:cub200.alpha}
    }
    \caption{PL exponent $\alpha$ versus reported Top1 Test Accuracies for pretrained DNNs available for different datasets (as segmented in Table~\ref{table:datasets}).
            }
    \label{fig:DSalphas}
\end{figure}

\begin{figure}[t]
    \centering
    \subfigure[ ResNet ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_01}
    }
    \subfigure[ SENet/SE-ResNet/SE-PreResNet/SE-ResNeXt ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_02}
    }
    \subfigure[ DIA-ResNet/DIA-PreResNet ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_03}
    }
    \subfigure[ ResNeXt ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_04}
    }
    \subfigure[ WRN ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_05}
    }
    \subfigure[ DLA ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_06}
    }
    \subfigure[ PreResNet ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_07}
    }
    \subfigure[ ProxylessNAS ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_08}
    }
    \subfigure[ VGG/BN-VGG ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_09}
    }
    \subfigure[ IGCV3 ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_10}
    }
    \subfigure[ EfficientNet ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_11}
    }
    \subfigure[ SqueezeNext/SqNxt ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_12}
    }
    \subfigure[ ShuffleNet ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_13}
    }
    \subfigure[ DRN-C/DRN-D ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_14}
    }
    \subfigure[ ESPNetv2 ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_15}
    }
    \subfigure[ HRNet ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_16}
    }
    \subfigure[ SqueezeNet/SqueezeResNet ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_17}
    }
    \caption{PL exponent $\alpha$ versus reported Top1 Test Accuracies for pretrained DNNs available for different architecture series (as segmented in Table~\ref{table:architectures}).
            }
    \label{fig:ARCHalphas}
\end{figure}

@@

>>>>

%%\begin{figure}[t]
%%    \centering
%%    \subfigure[ImageNet 1K]{
%%        \includegraphics[width=4.9cm]{img/all-imagenet-1k_alpha.png}
%%        \label{fig:imagenet1k-alpha}
%%    }
%%    \qquad
%%    \subfigure[ CIFAR 10 ]{
%%        \includegraphics[width=4.9cm]{img/all-cifar-10_alpha.png}
%%        \label{fig:cifar10.alpha}
%%    }
%%    \qquad
%%    \subfigure[ CIFAR 100 ]{
%%        \includegraphics[width=4.9cm]{img/all-cifar-100_alpha.png}
%%        \label{fig:cifar100.alpha}
%%    }
%%    \qquad
%%    \subfigure[ SVHN ]{
%%        \includegraphics[width=4.9cm]{img/all-svhn_alpha.png}
%%        \label{fig:svhn.alpha}
%%    }
%%    \qquad
%%    \subfigure[ CUB 200 ]{
%%        \includegraphics[width=4.9cm]{img/all-cub-200-2011_alpha.png}
%%        \label{fig:cub200.alpha}
%%    }
%%    \caption{PL exponent $\alpha$ versus reported Top1 Test Accuracies for pretrained DNNs available for different datasets (as segmented in Table~\ref{table:datasets}).
%%            }
%%    \label{fig:DSalphas}
%%\end{figure}
%%
%% 
%%\begin{figure}[t]
%%    \centering
%%    \subfigure[ ResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_01}
%%    }
%%    \subfigure[ SENet/SE-ResNet/SE-PreResNet/SE-ResNeXt ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_02}
%%    }
%%    \subfigure[ DIA-ResNet/DIA-PreResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_03}
%%    }
%%    \subfigure[ ResNeXt ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_04}
%%    }
%%    \subfigure[ WRN ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_05}
%%    }
%%    \subfigure[ DLA ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_06}
%%    }
%%    \subfigure[ PreResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_07}
%%    }
%%    \subfigure[ ProxylessNAS ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_08}
%%    }
%%    \subfigure[ VGG/BN-VGG ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_09}
%%    }
%%    \subfigure[ IGCV3 ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_10}
%%    }
%%    \subfigure[ EfficientNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_11}
%%    }
%%    \subfigure[ SqueezeNext/SqNxt ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_12}
%%    }
%%    \subfigure[ ShuffleNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_13}
%%    }
%%    \subfigure[ DRN-C/DRN-D ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_14}
%%    }
%%    \subfigure[ ESPNetv2 ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_15}
%%    }
%%    \subfigure[ HRNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_16}
%%    }
%%    \subfigure[ SqueezeNet/SqueezeResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_17}
%%    }
%%    \caption{PL exponent $\alpha$ versus reported Top1 Test Accuracies for pretrained DNNs available for different architecture series (as segmented in Table~\ref{table:architectures}).
%%            }
%%    \label{fig:ARCHalphas}
%%\end{figure}

@@

\begin{figure}[t]
    \centering
    \subfigure[ XXX, XXX ]{
        \includegraphics[width=3.7cm]{img/hex.png}
        \label{fig:summary_regressions_A_01}
    }
    \subfigure[ XXX, XXX ]{
        \includegraphics[width=3.7cm]{img/hex.png}
        \label{fig:summary_regressions_A_02}
    }
    \subfigure[ XXX, XXX ]{
        \includegraphics[width=3.7cm]{img/hex.png}
        \label{fig:summary_regressions_A_03}
    }
    \subfigure[ XXX, XXX ]{
        \includegraphics[width=3.7cm]{img/hex.png}
        \label{fig:summary_regressions_A_04}
    }
    \subfigure[ XXX, XXX ]{
        \includegraphics[width=3.7cm]{img/hex.png}
        \label{fig:summary_regressions_A_05}
    }
    \subfigure[ XXX, XXX ]{
        \includegraphics[width=3.7cm]{img/hex.png}
        \label{fig:summary_regressions_A_06}
    }
    \subfigure[ XXX, XXX ]{
        \includegraphics[width=3.7cm]{img/hex.png}
        \label{fig:summary_regressions_A_07}
    }
    \subfigure[ XXX, XXX ]{
        \includegraphics[width=3.7cm]{img/hex.png}
        \label{fig:summary_regressions_A_08}
    }
    \subfigure[ XXX, XXX ]{
        \includegraphics[width=3.7cm]{img/hex.png}
        \label{fig:summary_regressions_A_09}
    }
    \subfigure[ XXX, XXX ]{
        \includegraphics[width=3.7cm]{img/hex.png}
        \label{fig:summary_regressions_A_10}
    }
    \subfigure[ XXX, XXX ]{
        \includegraphics[width=3.7cm]{img/hex.png}
        \label{fig:summary_regressions_A_11}
    }
    \subfigure[ XXX, XXX ]{
        \includegraphics[width=3.7cm]{img/hex.png}
        \label{fig:summary_regressions_A_12}
    }
    \caption{Regression plots for model-dataset pairs, based on data from Table~\ref{table:MSEresults}, Table~\ref{table:R2results}, and Table~\ref{table:KTresults}.
             Each row corresponds to a different dataset-model pair:
             imagenet-1k and ResNet; 
             imagenet-1k and EfficientNet; and 
             imagenet-1k and PreResNet, repsectively.
             Each column column corresponds to a different metric:
             $\langle\log\Vert\cdot\Vert_{F}\rangle$; 
             $\langle\log\Vert\cdot\Vert_{\infty}\rangle$; 
             $\hat{\alpha}$; and
             $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$, repsectively.
            }
    \label{fig:summary_regressions_A}
\end{figure}
